\Large \bf \projtitle

### 2015-05-07 doc/paper/paper.tex
started reddit section

\section{Introduction}
It is common for personal blogs and other small websites to gain sudden attention
on large, high-traffic websites such as Reddit. Since these websites usually
experience much smaller traffic loads, the hardware devoted to hosting them
is typically not powerful enough to cope with this large influx of content requests.
These sudden, unexpected bursts of traffic often result in websites loading at
extremely slow speeds, or not loading at all, and is colloquially known as the
"Reddit Hug of Death". \\

@@

Due to limitations

>>>>

\section{Introduction}
It is common for personal blogs and other small websites to gain sudden attention
on large, high-traffic websites such as Reddit. Since these websites usually
experience much smaller traffic loads, the hardware devoted to hosting them
is typically not powerful enough to cope with this large influx of content requests.
These sudden, unexpected bursts of traffic often result in websites loading at
extremely slow speeds, or not loading at all, and is colloquially known as the
"reddit hug of death" or the "reddit effect." \\

@@

Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
bandwidth of the central server hosting the desired resource.
